The SMT Competition 2015--2018

### 2019-04-13 2018/report/SMT-COMP.tex
Benchmark weights, minor

SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation of SMT-COMP and SMT-LIB found that this
``significantly lessens the ability of a competition to determine
`best' solvers.''~\cite{CSW15} Together with the increased
computational resources available to the competition since its move to
StarExec, this finding prompted a paradigm shift.  Since 2015, the
competition is evaluating all solvers on all eligible benchmarks.
This change had an unintended side effect: the pseudo-random selection
process had been purposely constrained to choose benchmarks from
different benchmark families (that is, groups of benchmarks with
similar characteristics).  Since there are vast differences in size
between benchmark families in the SMT Library, the competition
since~2016 uses a scoring method that assigns a weight to each
Main-track benchmark in order to de-emphasize large benchmark
families~\cite{rules18}.

@@

A contentious issue with this ranking has been the scoring of
incorrect solver responses.  In the division rankings, an incorrect
response causes a solver to be ranked below all correct solvers for
that division.  But the competition's Main track consists of many
independent divisions.  To balance the strong interest in correct
solvers against the risk of stifling innovation, the competition-wide
ranking was revised in~2017 to use a fixed numeric penalty for each
division with incorrect responses.  The value of this penalty is
currently set so that entering a (possibly buggy) solver that can
solve all benchmarks into a division has a positive expected score if
the probability that a soundness bug in the solver will be triggered
is below~$20\,\%$.~\cite{rules18}

>>>>

SMT Competitions until~2014 employed a pseudo-random selection process
to further cull the number of benchmarks used in the competition.
However, a 2013 evaluation of SMT-COMP and SMT-LIB found that this
``significantly lessens the ability of a competition to determine
`best' solvers.''~\cite{CSW15} Together with the increased
computational resources available to the competition since its move to
StarExec, this finding prompted a paradigm shift.  Since 2015, the
competition is evaluating all solvers on all eligible benchmarks.
This change had an unintended side effect: the pseudo-random selection
process had been purposely constrained to choose benchmarks from
different benchmark families (that is, groups of benchmarks with
similar characteristics).  Since there are vast differences in size
between benchmark families in the SMT Library, the competition
since~2016 uses a scoring method that assigns a weight to each
Main-track benchmark in order to de-emphasize large benchmark
families~\cite{rules18}.  A benchmark's weight is computed as $(1 +
\ln F)/F$, where~$F\geq 1$ is the size of the benchmark's family.  The
log scaling seems a reasonable compromise between linearly combining
numbers of benchmarks, which would overemphasize large families, and
simply averaging the fraction of benchmarks solved, which would
overemphasize small families.

@@

A contentious issue with this ranking has been the scoring of
incorrect solver responses.  In the division rankings, an incorrect
response causes a solver to be ranked below all correct solvers for
that division.  But the competition's Main track consists of many
independent divisions.  A solver bug that affects one division need
not manifest itself in other divisions.  To balance the strong
interest in correct solvers against the risk of stifling innovation,
the competition-wide ranking was revised in~2017 to use a fixed
numeric penalty for each division with incorrect responses.  The value
of this penalty is currently set so that entering a (possibly buggy)
solver that can solve all benchmarks into a division has a positive
expected score if the probability that a soundness bug in the solver
will be triggered is below~$20\,\%$.~\cite{rules18}
